Capstone Movielens Report

### 2025-12-07 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
UMGYE Model Regularization: Support Functions: section removed.

#### UMGYE Model Regularization: Support Functions
\

::: {.noteblock data-latex=""}
The [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L128) function described below are defined in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L127) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L128) script.
:::

##### [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#128) Function {#func.regularize.test_lambda.UMGY_effect.cv}
\

This function calculates _RMSE_ of the _UMGYE Model_ using _5-Fold Cross Validation_ for the given $\lambda$ parameter value:
```{r, eval=FALSE}
regularize.test_lambda.UMGY_effect.cv <- function(lambda){
  if (is.na(lambda)) {
    stop("Function: regularize.test_lambda.UMGY_effect.cv
`lambda` is `NA`")
  }

  train_UMGY_effect.cv(lambda) |>
    calc_UMGY_effect_RMSE.cv()
}
```

::: {.noteblock data-latex=""}
Note that we reuse the function [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) calling it from the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv), but now with the $\lambda$ parameter different from the default ('lambda = 0') value.
:::

@@

Let's perform the preconfiguration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:

>>>>

@@

Let's perform the pre-configuration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:
